---
title: "School Shootings as of 2022"
author: "Simranjit Singh, Ashwin Subramanian, Isaac Keen, Rishita Reddy"
date: "11/17/2022"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, echo=FALSE, warning=FALSE, message=FALSE}

source("../source/summary_info.R")
summary_info
```
This summary file holds five important data points that relate to our data set about school shootings in the United States between 1990 and 2022. Total shootings, area type with the most shootings, type of school with the most shootings, state with the highest number of shootings and the highest fatalities in one shooting were all measured in this summary. As seen there were a total of 754 school shootings between 1990 and 2022. There were also the highest number of shootings in urban locations compared to rural and suburban areas. High schools had the highest number of shootings as well. The state with the most shootings was California and the highest number of fatalities in one shooting between 1990 and 2022 was 33.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/state_table.R")
state_table
```

This table categorizes shootings in the Unites States since 1990 based on the state. Texas has had 57 shootings since 1990 making Texas the state with the highest number of shootings. Maine, New Hampshire, Rhode Island, South Dakota, and Virgins Islands only had 1 shooting each since 1990. Most of these states are smaller states and are located on the east coast.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/pie_chart.R")
pie_chart()
```


This pie chart shows the number of shootings in different area types across the United States. As seen by the chart, urban areas had the most shootings, followed by suburban areas, followed by rural areas. The number of shootings between 1990 and today in urban areas was 256, 102 in suburban areas, and 23 in rural areas.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/bar_graph.R")
bar_graph
```


This bar graph displays the number of shootings based on the types of school. It categorizes school into 4 categories which are college, high school, middle school, and elementary school. High schools have the most shootings at 438 shootings since 1990, colleges had 152 shootings, middle schools have had 94 shootings, and elementary schools have had 57 shootings.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/line_graph.R")
fatalitiygraph
```


This line graph shows shootings in the United States since 1990 based on the date. As seen, there were 0 shootings in 1990, but after that they kept increasing for most part. Between 1995 and 2005, the number of school shootings were relatively low and between 2006 and 2014 they were high. The data shows two high spikes in school shootings in 2007 and 2012 and also shows that shootings are slowly increasing today.
